Analyzing Fairness: Race, Recidivism, and the COMPAS Algorithm

### 2022-04-08 final_metrics_analysis.Rmd

---
title: "COMPAS Race Analysis"
author: "Elisabeth Nesmith"
date: "3/8/2022"
output: html_document
---

>>>>

---
title: "Analyzing Fairness: Race, Recidivism, and the COMPAS Algorithm"
author: "Elisabeth Nesmith, Eunice Kim, Emma Kornberg, Amrita Acharya, Dianne Caravela"
date: "3/8/2022"
output: html_document
---
